Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-07 ms/manuscript.Rmd
Remove ecostructure analysis from plan and MS

loadd(list = c(
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns_8L"
),
cache = ja_fern_cache)

@@

```{r ecostructure}
tweak <- 0.75

sites <- ses_div_ferns_spatial %>%
  pull(grids)

centroids <-
ses_div_ferns_spatial %>%
  select(geometry) %>%
  mutate(centroid = sf::st_centroid(geometry)) %>%
  sf::st_coordinates(x = .$centroid) %>%
  as_tibble() %>%
  mutate(site = sites)

omega <-
species_motifs_ferns_8L$omega %>%
  as.data.frame %>%
  rownames_to_column("site") %>%
  left_join(centroids, by = "site") %>%
  column_to_rownames("site")

omega_centroids <- select(omega, X, Y) %>% # longitude, latitude
  as.matrix()

omega <- select(omega, -X, -Y)

ecos_plot_pie2(
    omega = omega,
    image_width = 6000*tweak,
    image_height = 4800*tweak,
    radius = 0.08,
    no_map = TRUE,
    coords = omega_centroids,
    long_lim = c(121, 148),
    lat_lim = c(23, 47),
    color = carto_pal(8, "Bold"),
    blank_bg = "grey90",
    path = here::here("results/species_motifs_ferns.png")
)

![](`r here::here("results/species_motifs_ferns.png")`)

**`r figure("ecostructure")`**. `r figure_cap("ecostructure")`. Pie charts represent the proportional contribution of each site to each of *k* = 8 spatial motifs, fit with a grade-of-membership model based on the community matrix using the R package \package{ecostructure}.

>>>>

loadd(list = c(
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny"
),
cache = ja_fern_cache)

@@
